The effect of climate forcing on numerical simulations of the Cordilleran ice sheet at the Last Glacial Maximum

### 2014-04-01 reviews/disc-ac1.tex
Polish the responses and add polite words

In fact, no. In Figs.~8 and~9 of the discussion paper, temperature climatologies are compared without lapse-rate correction. Due to differences in resolution of surface topography between climatological datasets used, this caused appearance of numerous topographic artefacts in Fig.~9. Following your comment, we produced updated figures that include a lapse-rate correction of 6\,{$^\circ$}C\,km$^{-1}$, as applied in the simulations.

The implementation of a lapse-rate correction in Fig.~9 (temperature difference maps, Fig.~AC1) results in smoother temperature difference maps, where effective temperature discrepancies are no longer overshadowed by local topographic anomalies (Fig.~AC2). Because temperature differences in this new map are much reduced, we adjusted colour scaling to emphasize smaller values.

@@

However you raise here a valid concern regarding potential ice sheet evolution to more similar states when accounting for precipitation changes, not considered in the current version of our manuscript. More particularly, in the east, where in most of our simulations, the ice margin does not attain a steady-state configuration, its position after 10\,kyr is largely determined by its rate of advance during the simulation length, which in turn depends on the amount of precipitation received. We agree that precipitation corrections in this region could slow down the ice margin advance, resulting in more similar configuration after 10\,kyr. We have included a discussion of this effect in Sect.~5.5.

@@

@@

\begin{figure}
    \centering
    \caption{Summer temperature density maps, after bilinear interpolation.}
    \includegraphics[width=70mm]{cordillera-climate-tempheatmap+nolr}
\end{figure}

>>>>

In fact, no. In Figs.~8 and~9 of the discussion paper, temperature climatologies are compared without lapse-rate correction. Due to differences in resolution of surface topography between climatological datasets used, this caused appearance of numerous topographic artefacts (Fig.~AC1). Following your comment, we produced updated figures that include a lapse-rate correction of 6\,{$^\circ$}C\,km$^{-1}$, as applied in the simulations.

The implementation of a lapse-rate correction in Fig.~9 (temperature difference maps) results in smoother maps, where effective temperature discrepancies are no longer overshadowed by local topographic anomalies (Fig.~AC2). Because temperature differences in this new map are much reduced, we adjusted colour scaling to emphasize smaller values.

@@

We think that you raise here a valid concern. In the east, where in most of our simulations, the ice margin does not attain a steady-state configuration, its position after 10\,kyr is largely determined by its rate of advance during the simulation length, which in turn depends on the amount of precipitation received. We agree that precipitation corrections in this region could slow down the ice margin advance, resulting in more similar configuration after 10\,kyr. We have included a discussion of this effect in Sect.~5.5.

@@

Thank you again for your positive comments and constructive input.

@@

\begin{figure}
    \centering
    \includegraphics[width=70mm]{cordillera-climate-tempheatmap+nolr}
    \caption{Summer temperature density maps, after bilinear interpolation.}
\end{figure}

### 2014-04-01 reviews/disc-ac2.tex
Polish the responses and add polite words

Thank you very much for reading and positively commenting on our manuscript. We apologize for the lack of detail regarding isostatic issues, which we discuss below.

@@

@@

Thank you for noticing this mistake. We have corrected it.

>>>>

Thank you very much for reading our manuscript and positively commenting on it. We apologize for the lack of detail regarding isostatic issues, which we discuss below.

@@

We have emphasized the fact that bed elevation does not reach equilibrium at the beginning of Sect.~5.4.

\msquote{Most of the simulations presented in this study, and more particularly those that reproduce the LGM ice margin more closely (Fig.~15) do not reach a steady-state. Instead, rates of growth remain high throughout the run, and bed elevation does not come close to equilibrium with the ice load.}

@@

Thank you for noticing this mistake. We have corrected it (in Figs.~8 and~10).

In general, thank you again for this supportive and constructive review.
